Finite Property Convex Elicitation Notes

### 2018-04-09 cvx-fin-notes.tex
Added my (Jessie) questions to notes file

>>>>

\jessie{Notes partially for myself, but also with some questions I'm not sure of.  Feel free to correct}
\section{2-d case}
We want some (invertible) representation $\phi: \reals^2 \to \reals$ so that $\forall p \in \P$, $\Gamma(p) = \phi([ x_1, x_2 ])$.

We want $\Gamma(p) = \phi(x) = \argmin_r \E_p L(r, Y)$

\subsection{Geometric median}
Consider $\Gamma(p) = \argmin E_p ||r - Y ||_2$
Let $\phi(x)$ be the representation of $\Gamma(p)$ in $\reals^n$.
Can we represent $\phi$ in some lower dimensional manner so that $\phi(x) = \Gamma(p)$ for all $p \in \P$?

The level sets of the geometric median intersect (see the git repo) so it's not elicitable.

Can we/do we want to construct a voronoi diagram of the geometric median?
